---
title: "Last updated `r format(Sys.Date(), '%d %B %y')`"
output:
  html_document:
    number_sections: false
    classoption: landscape
---

```{r setup, include = FALSE}
# setup
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(scholar))
source(here::here("R", "_default_DT.R"))
source(here::here("R", "_flextable_defaults.R"))
googlesheets4::gs4_auth(email="janick.weberpals@gmail.com")
sheet_url <- Sys.getenv("GOOGLESHEETS_URL")
## google scholar id
gs_id <- 'B59js_8AAAAJ&hl=en'
## google scholar profile
gs_profile <- scholar::get_profile(gs_id)
# set chunk default options
knitr::opts_chunk$set(dpi = 100, 
                      echo = FALSE,
                      fig.align = "left")
```

This section presents an overview of publications. The formatting and listing is compliant with the [specifications required](https://fa.hms.harvard.edu/faculty-medicine-cv-guidelines) for a faculty appointment at Harvard Medical School and ordered chronologically from earliest to most recent.

For more information you can find my **orcid** website here: https://orcid.org/0000-0003-0404-7394

## Peer-Reviewed Publications in Print or Other Media

```{r, message=FALSE}
# get publications from own database
pubs <- googlesheets4::read_sheet(sheet_url, sheet = 'Manuscripts')
```

### Research investigations

```{r}
pubs %>% 
  dplyr::filter(paragraph == "Research investigations") %>% 
  dplyr::filter(status %in% c("Published", "Accepted")) %>% 
  papers_tbl()
```

\* indicates co-first or co-senior authorship. <br>
\*\* indicates that mentee is first or co-first author 

## Non-Peer Reviewed Scientific or Medical Publications in Print or Other Media

### Reviews, chapters, monographs and editorials

```{r}
pubs %>% 
  dplyr::filter(paragraph == "Reviews chapters monographs and editorials (non peer-reviewed)") %>% 
  dplyr::filter(status %in% c("Published", "Accepted")) %>% 
  papers_tbl()
```

### Letters to the Editor
```{r}
pubs %>% 
  dplyr::filter(paragraph == "Letters to the Editor  (non peer-reviewed)") %>% 
  dplyr::filter(status %in% c("Published", "Accepted")) %>% 
  papers_tbl()
```

## Thesis

**Weberpals J.** Associations between β-blocker exposure and cancer prognosis: the role of immortal time bias and analytical approaches in pharmacoepidemiological studies on cancer patient survival. [Doctor Scientiarum Humanarum Dissertation], Medical Faculty of Heidelberg, Rupert Carola University Heidelberg, Germany; 2018

## Abstracts, Poster Presentations and Exhibits Presented at Professional Meetings

```{r}
pubs %>% 
  dplyr::filter(paragraph == "Abstracts Poster Presentations and Exhibits Presented at Professional Meetings") %>% 
  dplyr::filter(
    dplyr::between(year, lubridate::year(Sys.Date()) - 3, lubridate::year(Sys.Date())) &
      If_abstract_published_manuscript == FALSE | 
      manuscript_type %in% c("Co-author oral presentation", "Poster spotlight")) %>% 
  papers_tbl()
```
