---
title: "Last updated `r format(Sys.Date(), '%d %B %y')`"
output:
  html_document:
    number_sections: false
    classoption: landscape
---

```{r setup, include = FALSE}
# setup
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(scholar))
source(here::here("R", "_default_DT.R"))
source(here::here("R", "_flextable_defaults.R"))
googlesheets4::gs4_auth(email="janick.weberpals@gmail.com")
sheet_url <- Sys.getenv("GOOGLESHEETS_URL")
## google scholar id
gs_id <- 'B59js_8AAAAJ&hl=en'
## google scholar profile
gs_profile <- scholar::get_profile(gs_id)
# set chunk default options
knitr::opts_chunk$set(dpi = 100, 
                      echo = FALSE,
                      fig.align = "left")
```

This section presents an overview of presentations and scientific talks The formatting and listing is compliant with the [specifications required](https://fa.hms.harvard.edu/faculty-medicine-cv-guidelines) for a faculty appointment at Harvard Medical School and ordered chronologically from earliest to most recent.

## Report of Regional, National and International Invited Teaching and Presentations
 
### Invited Presentations and Courses

*Those presentations below sponsored by outside entities are so noted and the sponsor is identified in parentheses.*

##### Regional
```{r, eval=F}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Invited presentation") %>% 
  dplyr::filter(geographics == "Regional")
```
None to display yet

#### Regional Abstract Oral Presentations
```{r, eval=F}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Abstract oral presentation") %>% 
  dplyr::filter(geographics == "Regional")
```
None to display yet

#### National
```{r}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Invited presentation") %>% 
  dplyr::filter(geographics == "National") %>% 
  presentations_tbl()
```

#### National Abstract Oral Presentations
```{r}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Abstract oral presentation") %>% 
  dplyr::filter(geographics == "National") %>% 
  presentations_tbl()
```


#### International
```{r}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Invited presentation") %>% 
  dplyr::filter(geographics == "International") %>% 
  presentations_tbl()
```

#### International Abstract Oral Presentations
```{r}
pubs %>% 
  dplyr::filter(paragraph == "Report of Regional National and International Invited Teaching and Presentations") %>% 
  dplyr::filter(manuscript_type == "Abstract oral presentation") %>% 
  dplyr::filter(geographics == "International") %>% 
  presentations_tbl()
```
